Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-07 cross_compilation.tex
Add label for cross_compilation sectio and correct typos

%\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}

Some processing expensive tasks such as compiling code libraries can with
advantage be performed in a \ac{PC} rather than a \ac{Raspi} to save time.
This section will present how to setup a toolchain in a \ac{PC} that may
be used to cross compile C++ code to run in \ac{Raspi}s.
There will be given an example of compiling a simple C++ application to run
on \ac{Raspi}, but also how Kodo-cpp can be cross compiled for \ac{Raspi}.

>>>>

%\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
\label{sec:cross_compilation}
Some processing expensive tasks such as compiling code libraries can with
advantage be performed in a \ac{PC} rather than a \ac{Raspi} to save time.
This section will present how to setup a toolchain in a \ac{PC} that may
be used to cross compile C++ code to run in \ac{Raspi}s.
There will be given an example of compiling a simple C++ application to run
on \ac{Raspi}, but also how Kodo-cpp can be cross compiled for \ac{Raspi}.

### 2016-06-07 introduction.tex
Add label for cross_compilation sectio and correct typos

Our work is organized as follows. Section~\ref{sec:testbed} introduces the
testbed system, its setup, files configuration, connectivity and compilation of
the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
in our study. Later, in Section~\ref{sec:metrics} we describe the considered
metrics and methodology for performance comparison of the codes deployed in
the \ac{Raspi}. In Section~\ref{sec:measurements}, we show the measurements in
the \ac{Raspi} models of the mentioned metrics. Final conclusions and future work
are reviewed in Section~\ref{sec:conclusions}.

>>>>

Our work is organized as follows. Section~\ref{sec:testbed} introduces the
testbed system, its setup, files configuration and connectivity.
Section~\ref{sec:cross_compilation} elaborates on the compilation of
the Kodo library for the \ac{Raspi}. Section~\ref{sec:schemes} defines the
coding schemes employed in our study. Later, in Section~\ref{sec:metrics}
we describe the considered metrics and methodology for performance comparison
of the codes deployed in the \ac{Raspi}. In Section~\ref{sec:measurements}, we
show the measurements in the \ac{Raspi} models of the mentioned metrics. Final
conclusions and future work are reviewed in Section~\ref{sec:conclusions}.

### 2016-06-07 metrics.tex
Add label for cross_compilation sectio and correct typos

Once defined the coding schemes behavior in terms of encoding
and decoding, we proceed to describe the metrics considered in our study.
The goodput is a measure for the effective processing speed since it
excludes protocol overhead but considers all delays related with
algorithmic procedures, field operations, hardware processing, multicore
coordination (where it applies), etc. Moreover, encoding and decoding
goodput permits to observe if coding is a system-block that limits the
end-to-end performance. If a system presents a low goodput, this will
affect the \ac{QoE} of delay-intolerant applications for the end user.
For example, mobile user applications are typically delay-intolerant.
Furthermore, \ac{Raspi} processors are based in the \ac{ARM} architecture
which is the same as in mobile devices such as smartphones or tables.
Thus, the \ac{Raspi} might be used as an experimental tool to get an
estimate of a mobile device processing capability which is easy-deployable
and at a much lower cost than a smartphone.

>>>>

Once defined the coding schemes behavior in terms of encoding
and decoding, we proceed to describe the metrics considered in our study.
The goodput is a measure for the effective processing speed since it
excludes protocol overhead but considers all delays related with
algorithmic procedures, field operations, hardware processing, multicore
coordination (where it applies), etc. Moreover, both encoding and decoding
goodput permit to observe if coding is a system-block that limits the
end-to-end performance. If a system presents a low goodput, this will
affect the \ac{QoE} of delay-intolerant applications for the end user.
For example, mobile user applications are typically delay-intolerant.
Furthermore, \ac{Raspi} processors are based in the \ac{ARM} architecture
which is the same as in mobile devices such as smartphones or tablets.
Thus, the \ac{Raspi} might be used as an experimental tool to get an
estimate of a mobile device processing capability which is easy-deployable
and at a much lower cost than a smartphone.
